Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-25 paper/ms.tex
referencias, conclusiones

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
observational estimates.
However, we find that the same individual models have a relatively tight
$1\sigma$ mass gap $\Delta M_{1\sigma}\approx 0.4$ dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
\end{abstract}

@@

From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
The $1\sigma$ uncertainty for this median value is estimated from the
$16$ and $84$ percentile values in the $\log M_{50}$ distribution.  
This result is consistent with previous
 estimations of  the  median dark matter halo mass reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6}$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9}$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}}$) 
using semi-analitical approaches.   MENTION THAT OUR MASS IS SYSTEMATICALLY LOWER
AND THAT (ONLY IF MAKE SENSE) WE DO NOT DISAGREE  THAT DARK MATTER OF BIELBY AND OTHERS  OF THEIR PARTICULAR FIELDS IRE WRONG, BUT WHEN THE COSMIC VARIANCE IS INCLUDES THAT IMPLIES THAT THA THE MEAIN MASS OF LAES IN THE UNIVERSE IS SMALLER (BECAUSE OF THE ASSIMETRY IN THE NUMBER DENSITY DISTRIBUTION FUNCTION). DO SEMIANALITIC MODELS ASSUME GAUSSIAN DISTRIBUTION OF MATTER PERTURBATIONS?

However, the same Figure \ref{fig:mmed} shows something 
that semi-analytical approaches were not able to predict.
The mass width, $\Delta \log M_{1\sigma}$, that is the width of the mass
distribution for a given model with fixed $\mmin$ and $\mmax$, has a
median value and $1\sigma$ uncertainty of $\Delta \log M_{1\sigma} =
0.55^{+0.11}_{-0.31}$ dex.
This means that the mass range for halos hosting LAEs is very narrow.
There is only a factor of $2$ to $4$ between the lower and upper mass
boundary of the central 68 percentile of the mass distribution. 
\todo HERE WE NEED TO CLARIFY THAT MMAX CAN BE STILL VERY 
LARGE BECAUSE OF THE ASSYMETRY IN THE DARK MATTER HALO MASS 
FUNCTION MAYBE MENTIONING THE 2-SIGMA WIDTH THAT IS WAY MUCH 
HIGHER THAN THE 1-SIGMA WIDTH. THIS IS ACTUALLY THE REASON FOR 
THE POOR CONSTRAIN THAT WE OBTAIN IN MMAX BUT IT IS STILL IMPORTANT
BECAUSE IT DETRMINES THE  STRENGTH OF THE CLUSTERING AT SHORT SCALES.

@@

\subsection{Constraining Dark matter halos mass  with cosmic variance}
Fig. \ref{fig:cosmicv0}  shows the  halo number distribution (HND) in
the  mock fields of the simulation for different models
$\mathcal{M}$. By simple inspection one can infer an increase in the
distribution with as \lmmin\ increases.  This trend is confirmed in
Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue
diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function
of \lmmin. We particularly found that when we consider survey fields
of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of
the HND increases monotonically from 0.05dex (0.10dex) when
$\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter
result opens the possibility to constrain the \lmmin (as well as the
median mass) of LAEs by simply measure the width of the distribution
of observed LAE along several observational fields mapping $\sim1{\rm
  deg^2}$ in area and the observational depth determined by the NB479
filter.

@@

In this letter we studied the impact of cosmic variance and
observational uncertainties in constraining the mass range and
occupation fraction of dark matter halos hosting  LAEs.   
To this end we used the BolshoiP N-body simulation to construct  27 mock fields
with the same typical size  of observed fields at $z=3.1$ ($\sim 1
{\rm deg^2}$).      
In our model a dark matter halo with mass in the range $M_{\rm
  min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE
at most.  
We explored the parameter space determined by \mmin\ and \mmax\ using
Monte Carlo Markov-Chain minimization to match the observed  ACF and
mean number density of LAEs.    
It is the first time that such a thorough exploration of the cosmic
variance impact on LAEs statistics is presented in the literature.

We find that once cosmic variance is taken into account, the
observational data can only put weak constraints on \ \mmax\ and \focc. 
When we translate these loos constraints into the median mass, we find
a general consistency with previous works \citep{Hayashino2004,
  Gawiser07,Ouchi2008} specially with the most recent one
\citep{Bielby16}.

Nevertheless, our analysis allowed us to draw three results that can
be used to put tighter constraints on \mmin and \focc once
upcoming large LAE surveys, such as the HETDEX project 
\citep{Hetdex2011} and the HSC ultra deep survey, are available:

@@

\item The width of the LAE number distribution function
  obtained over several fields of $\approx 1$ deg$^2$ is tightly
  correlated with \mmin. That measurement with next generation surveys
  will be able to constrain \mmin within a factor of $\sim 2$.

We also find that the 1-$\sigma$ width of the mass distribution is
highly constrained to be between $0.2$ and $0.6$ dex. 
This result imposes constraints on different models for LAEs formation
in a cosmological context as to why observable LAEs are constrained
into a narrow halo mass range.

Overall, our approach highlights the importance of forward modelling
to take explicitly into account the effects of cosmic variance.
We expect this

\end{enumerate}

@@

\bibliographystyle{apj}
%\bibliography{references.bib}
\begin{thebibliography}{38}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

>>>>

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
However, we find that the same individual models have a relatively tight
$1\sigma$ mass gap $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
\end{abstract}

@@

From this distribution we obtain $\log M_{50} = 10.5\pm 0.6$ or
equivalently $M_{50} = 3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.  
The $1\sigma$ uncertainty for this median value is estimated from the
$16$ and $84$ percentile values in the $\log M_{50}$ distribution.

Our result is consistent within the statistical uncertainties with
previous estimates reported by
 \citet{Bielby16} ($\tilde{M}_{\mathrm h} = 10^{11.0\pm0.6} \hMsun$),
 \citet{Gawiser07} ($\tilde{M}_{\mathrm h} = 10^{10.9\pm0.9} \hMsun$) and
 \citet{Ouchi2010} ($\tilde{M}_{\mathrm h} = 10^{10.8^{+1.8}_{-0.8}} \hMsun$) 
using semi-analitical approaches.   
In spite of the large uncertainties, we note that our median mass is
systematically below theirs by $0.3$ to $0.5$ dex.

However, the same Figure \ref{fig:mmed} shows something 
that semi-analytical approaches were not able to predict.
The mass width, $\Delta \log M_{1\sigma}$, that is the width of the mass
distribution for a given model with fixed $\mmin$ and $\mmax$, has a
median value and $1\sigma$ uncertainty of $\Delta \log M_{1\sigma} =
0.55^{+0.11}_{-0.31}$ dex.
This means that the mass range for halos hosting LAEs is very narrow.
There is only a factor of $2$ to $4$ between the lower and upper mass
boundary of the central 68 percentile of the mass distribution. 
We emphasize that \mmax\ can still be very large while the width is
small due to the asymetry in the dark matter halo mass function.

@@

\subsection{Constraining Dark matter halos mass  with cosmic variance}

Fig. \ref{fig:cosmicv0}  shows the  halo number distribution (HND) in
the  mock fields of the simulation for different models
$\mathcal{M}$. 
By simple inspection one can infer that the distribution width
increases with \mmin.

In Fig. \ref{fig:cosmicv} we confirm this trend by plotting the
HND $1\sigma$ width for good models ($\chi^{2}_{\mathcal{M}}/2 < 1$) as a function
of \lmmin. 
We find that considering all the mock $25$ field the $1\sigma$ width, $W_{1\sigma}$
increases with \mmin following

\begin{equation}
W_{1\sigma} = (0.138\pm 0.002) \times \left( \frac{\mmin}{10^{11}\hMsun} \right)^{0.177\pm0.009}.
\label{eq:width}
\end{equation}

This result opens the possibility to constrain the \lmmin (as well as the
median mass) of LAEs by simply measuring the width of the distribution
of observed LAE along several observational fields. 
This idea has been already explored for $z>6$ galaxies
\citep{Robertson10}.

To keep the validity of Eq. (\ref{eq:width}) there should at least be
$27$ fields (to follow the same numbers we use here) of size $\sim1{\rm
  deg^2}$ with the same observational coditions (filters, equivalent
width cuts). 
However, repeating the same kind of cosmic variance study for different
survey strategies should help to provide a constraint of the same
kind.

@@

In this letter we studied the impact of cosmic variance and
observational uncertainties in constraining the mass range and
occupation fraction of dark matter halos hosting  LAEs.   
To this end we used the BolshoiP N-body simulation to construct  27 mock fields
with the same typical size  of observed fields at $z=3.1$ ($\sim 1
{\rm deg^2}$).      
In our model a dark matter halo with mass in the range $\mmin
<M_{h}<\mmax$ can only host one detectable LAE at most.  
We explored the parameter space determined by \mmin\ and \mmax\ using
Monte Carlo Markov-Chain minimization to match the observed  ACF and
mean number density of LAEs.    
It is the first time that such a thorough exploration of the cosmic
variance impact on LAEs statistics is presented in the literature.

We find that once cosmic variance is taken into account, the
observational data can only put weak constraints on  \mmax\ and \focc. 
When we translate these loos constraints into the median mass, we find
a general consistency with previous works \citep{Hayashino2004,
  Gawiser07,Ouchi2008} specially with the most recent one
\citep{Bielby16}.

Nevertheless, our analysis allowed us to draw two results that can
be used to put tighter constraints on \mmin and \focc once
upcoming large LAE surveys, such as the HETDEX project 
\citep{Hetdex2011} and the HSC ultra deep survey, are available:

@@

\item The width of the LAE number distribution function
  obtained over several fields of $\approx 1$ deg$^2$ is tightly
  correlated with \mmin. 
  That measurement with next generation surveys
  will be able to constrain \mmin within a factor of $\sim 2$.
\end{enumerate}

We also find that the 1-$\sigma$ width of the mass distribution is
highly constrained to be between $0.2$ and $0.6$ dex. 
This result can be used to test different models for LAEs formation
in a cosmological context to better understand why observable LAEs are
constrained into a narrow halo mass range.

@@

\bibliographystyle{apj}
%\bibliography{references.bib}
\begin{thebibliography}{39}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Robertson}(2010)}]{Robertson10}
{Robertson}, B.~E. 2010, \apjl, 716, L229
